\Large \bf Polyglots : Crossing Origins by Crossing Formats

### 2013-05-08 main.tex
check point

\begin{abstract}
 In a heterogeneous system like the web, information is
exchanged between components in versatile formats. A new breed of attacks is on
the rise that exploit the mismatch between the expected and provided content.
% 
This paper identifies the root cause of a large class of attacks: \emph{polyglots}. 
A polyglot is a program that is valid in multiple programming languages. Polyglots allow
multiple interpretation of the content, providing a new space of attack vectors.
%
We characterize of what constitutes a dangerous format in the web setting and
identify particularly dangerous formats, with PDF as the prime example. We
demonstrate that polyglot-based attacks on the web open up for insecure
communication across Internet origins. 
%
The paper presents novel attack vectors that infiltrate the trusted
origin by \emph{syntax injection} across multiple languages and by
\emph{content smuggling} of
malicious payload that appears formatted as benign content. The
attacks lead to both \emph{cross-domain leakage} and \emph{cross-site
  request forgery}.
%
We perform a systematic study of
PDF-based injection and content smuggling attacks. We evaluate the current
practice in client/server content filtering and PDF readers for polyglot-based
attacks, and report on vulnerabilities in the top 100 Alexa web sites. Our
recommendations for protective measures on server side, in browsers, and in content
interpreters (in particular, PDF readers) show how to mitigate the attacks.
\end{abstract}

@@

\paragraph{Attack vectors}
\todo{Describe general scenario with forward pointer}
We present novel attack vectors that are based on (i)
\emph{syntax injection} that 
operate across multiple languages and on (ii) \emph{content smuggling} that supply
malicious payload that appears formatted as benign content. The
attacks lead to both \emph{cross-domain leakage} and \emph{cross-site
request forgery}.

@@

\paragraph{Evaluation and mitigation}
We evaluate the current
practice in client/server content filtering and PDF readers for polyglot-based
attacks, and report on vulnerabilities in the top 100 Alexa web sites. Our
recommendations for protective measures on server side, in browsers, and in content
interpreters (such as PDF readers) show how to mitigate the attacks.

@@

In recent versions of Adobe Reader certain measures has been taken to prevent 
creating PDF-based polyglots. In accordance with our recommendations Adobe Reader 
has made the parsing more strict by attempting to match the first bytes of the 
file against a set of known signatures. If 
a match is found, the parser will abort loading of the document. The problem of 
this approach is that there are a number of file formats that lack a reliable 
signature, e.g., HTML. Also, for this approach to be reliable, the signature 
must match the signature enforced by other interpreters of the format. A notable 
counter example is the signature used for the JPG format. While the signature is 
correct according to the specification of the format, several JPG interpreters
will allow slightly malformed signatures. Such a malformed signature will bypass 
the check in Adobe Reader and still be rendered correctly in a viewer. This opens up for PDF-based
polyglot attacks.

@@

\subsection{Alexa top 100}
We have conducted two
studies to evaluate the prevalence of the problem on popular sites, 
covering the Alexa top 100 websites. Because of their dominance 
on the web, these websites are also the most exposed to security threats.
The first study covers PDF-based polyglot attacks using syntax injection as the 
infiltration method; the second covers content smuggling.
%It does not involve polyglot attacks based on content smuggling, as 
%potential targets generally require authentication before submitting content.
We refrain from mentioning names of individual websites to prevent exploitation 
before the issues have been properly dealt with. Neither do we want to disclose 
these websites as particularly vulnerable. We are in contact with the teams responsible for the websites to help
mitigate the vulnerabilities.

\paragraph{Syntax injection}
The study is based on supplying the websites with the benign minimal PDF in 
Listing~\ref{lst:minimal-pdf}, and examining the corresponding responses to this input.
The sample contains the essential keywords and tokens required to perform a syntax 
injection based polyglot attack. If these tokens pass through unaltered, the website is 
considered vulnerable. The process has been conducted manually and only input 
parameters on publicly accessible pages, those that do not require authentication, 
were tested. Considering that most inputs are available only to authenticated 
users, the results suggests that more websites are likely vulnerable in input that do
require authentication.

The conclusion is 
that nine websites out of the hundred apply insufficient content filtering with 
respect to the PDF format. Out of the nine found to be vulnerable; five were 
susceptible to PDF based polyglot attacks, and four applied 
insufficient content filtering, but the input was reflected in a way that 
prevented exploitation, e.g. the header appeared after 1024 bytes.
%
%, which have the potential of compromising the 
%confidentiality and integrity of the website's users.
%

@@

\begin{enumerate}
\item The first web site reflected user input in an inline  
JavaScript context, inside a string. To prevent cross-site scripting in this 
context, the following measures were taken: the JavaScript string delimiters 
and the backslash character were properly escaped, and the 
string "$<$/script$>$" was removed. These measures are sufficient to protect against XSS attacks, 
but do not prevent an attacker 
from injecting valid PDF syntax.
\item The second website reflected the user input in an HTML-comment context. 
The only measure taken to prevent XSS attacks in this context was removing any 
occurrence of the character sequence "--$>$". Again, while successfully preventing 
XSS attacks, this measure is ineffective in preventing an attacker from injecting PDF syntax.
\end{enumerate}

\paragraph{Content smuggling}
Further, a smaller study was conducted, not covering the full Alexa top 100, but 
targeting popular cloud storage services. 
This study is based on polyglot content being uploaded to the service and 
subsequently analyzed to determine which origin it was served under. Two major 
enterprise cloud storage services were found to be susceptible to attacks. Both service makes an effort to
follow current best practices, see Section~\ref{sec:smuggling-mitigation}, but fail to cover scenarios for content upload.

>>>>

\begin{abstract}
 In a heterogeneous system like the web, information is
exchanged between components in versatile formats. A new breed of attacks is on
the rise that exploit the mismatch between the expected and provided content.
% 
This paper identifies the root cause of a large class of attacks: \emph{polyglots}. 
A polyglot is a program that is valid in multiple programming languages. Polyglots allow
multiple interpretation of the content, providing a new space of attack vectors.
%
We characterize of what constitutes a dangerous format in the web setting and
identify particularly dangerous formats, with PDF as the prime example. We
demonstrate that polyglot-based attacks on the web open up for insecure
communication across Internet origins. 
%
The paper presents novel attack vectors that infiltrate the trusted
origin by \emph{syntax injection} across multiple languages and by
\emph{content smuggling} of
malicious payload that appears formatted as benign content. The
attacks lead to both \emph{cross-domain leakage} and \emph{cross-site
  request forgery}.
%
We perform a systematic study of
PDF-based injection and content smuggling attacks. We evaluate the current
practice in client/server content filtering and PDF readers for polyglot-based
attacks, and report on vulnerabilities in the top 100 Alexa web
sites. 
%
We identify five web sites to be vulnerable to syntax injection
attacks. Further,
%
we have found two major 
enterprise cloud storage services to be susceptible to content
smuggling attacks.
%
Our
recommendations for protective measures on server side, in browsers, and in content
interpreters (in particular, PDF readers) show how to mitigate the attacks.
\end{abstract}

@@

\todo{Describe general scenario with forward pointer}
We present novel attack vectors that are based on (i)
\emph{syntax injection} that 
operate across multiple languages and on (ii) \emph{content smuggling} that supply
malicious payload that appears formatted as benign content. The
attacks lead to both \emph{cross-domain leakage} and \emph{cross-site
request forgery}.

@@

\paragraph{Evaluation and mitigation}
We evaluate the current
practice in client/server content filtering and PDF readers for polyglot-based
attacks, and report on vulnerabilities in the top 100 Alexa web
sites. 
%
Unfortunately, several major web sites do not protect against polyglot
attacks. Five out of the top 100 Alexa web sites are vulnerable to syntax injection
attacks. In addition,
we have found two major 
enterprise cloud storage services to be susceptible to content
smuggling attacks.
%
Our
recommendations for protective measures on server side, in browsers, and in content
interpreters (such as PDF readers) show how to mitigate the attacks.

@@

In recent versions of Adobe Reader certain measures have been taken to prevent 
creating PDF-based polyglots. In accordance with our recommendations, Adobe Reader 
has made the parsing more strict by attempting to match the first bytes of the 
file against a set of known signatures. If 
a match is found, the parser will abort loading of the document. 
However, this does not fully defend against PDF-based polyglot attacks.
The problem of 
this approach is that there are a number of file formats that lack a reliable 
signature, e.g., HTML. Also, for this approach to be reliable, the signature 
must match the signature enforced by other interpreters of the format. A notable 
counterexample is the signature used for the JPG format. While the signature is 
correct according to the specification of the format, several JPG interpreters
will allow slightly malformed signatures. Such a malformed signature will bypass 
the check in Adobe Reader and still be rendered correctly in a viewer. This opens up for PDF-based
polyglot attacks.

@@

\subsection{Alexa top 100}
We have conducted two
studies to evaluate the prevalence of the problem on popular sites, 
covering the Alexa top 100 web sites. Because of their dominance 
on the web, these web sites are also the most exposed to security threats.
The first study covers PDF-based polyglot attacks using syntax injection as the 
infiltration method; the second covers content smuggling.
%It does not involve polyglot attacks based on content smuggling, as 
%potential targets generally require authentication before submitting content.
We refrain from mentioning names of individual web sites to prevent exploitation 
before the issues have been properly dealt with. Neither do we disclose 
these web sites as particularly vulnerable. We are in contact with the teams responsible for the web sites to help
mitigate the vulnerabilities.

\paragraph{Syntax injection}
The study is based on supplying the web sites with the benign minimal PDF in 
Listing~\ref{lst:minimal-pdf}, and examining the corresponding responses to this input.
The sample contains the essential keywords and tokens required to perform a syntax 
injection based polyglot attack. If these tokens pass through unaltered, the web site is 
considered vulnerable. The process has been conducted manually and only input 
parameters on publicly accessible pages, those that do not require authentication, 
were tested. Considering that most inputs are available only to authenticated 
users, the results suggests that more web sites are likely vulnerable in input that do
require authentication.

The conclusion is 
that nine web sites out of the hundred apply insufficient content filtering with 
respect to the PDF format. Out of the nine found to be vulnerable; five were 
susceptible to PDF based polyglot attacks, and four applied 
insufficient content filtering, but the input was reflected in a way that 
prevented exploitation, e.g. the header appeared after 1024 bytes.
%
%, which have the potential of compromising the 
%confidentiality and integrity of the web site's users.
%

@@

\begin{enumerate}
\item The first web site reflected user input in an inline  
JavaScript context, inside a string. To prevent cross-site scripting in this 
context, the following measures were taken: the JavaScript string delimiters 
and the backslash character were properly escaped, and the 
string "$<$/script$>$" was removed. These measures are sufficient to protect against XSS attacks, 
but do not prevent an attacker 
from injecting valid PDF syntax.
\item The second web site reflected the user input in an HTML-comment context. 
The only measure taken to prevent XSS attacks in this context was removing any 
occurrence of the character sequence "--$>$". Again, while successfully preventing 
XSS attacks, this measure is ineffective in preventing an attacker from injecting PDF syntax.
\end{enumerate}

\paragraph{Content smuggling}
Further, a smaller study was conducted, not covering the full Alexa top 100, but 
targeting popular cloud storage services. 
This study is based on polyglot content being uploaded to the service and 
subsequently analyzed to determine which origin it was served
under. We have found two major 
enterprise cloud storage services to be susceptible to attacks. Both service makes an effort to
follow current best practices, see Section~\ref{sec:smuggling-mitigation}, but fail to cover scenarios for content upload.
